\pkg{sdmTMB}: An \proglang{R} Package for Fast, Flexible, and User-Friendly Generalized Linear Mixed Effects Models with Spatial and Spatiotemporal Random Fields

### 2023-09-18 doc/paper-jss/sdmTMB-paper.Rnw
Edits

Importantly, \texttt{dependencies = TRUE} includes the \proglang{R}-INLA
package \citep{rue2009, lindgren2011, lindgren2015}, which is not on CRAN but is
needed for the \texttt{make\_mesh()} function below. Soon, we intend to switch
to using the \pkg{fmesher} package to eliminate this dependency.

@@

There are several planned additions to the \pkg{sdmTMB} model structure.
A subset of features to be added in the near future includes (1) multivariate
models to allow for simultaneous modelling of data from multiple species, (2)
integration with the \pkg{RTMB} package so that the model code base will be
written in \proglang{R} rather than \proglang{C++}, (3) inclusion of
a dispersion formula similar to \pkg{glmmTMB}, and (4) estimation of random
slopes.
% TODO random slopes looks gnarly to do generically?

>>>>

Importantly, \texttt{dependencies = TRUE} includes the \proglang{R}-INLA
package \citep{rue2009, lindgren2011, lindgren2015}, which is not on CRAN but is
needed for the \texttt{make\_mesh()} function below. Soon, we intend to switch
to using the \pkg{fmesher} \citep{fmesher} package to eliminate this dependency.

@@

There are several planned additions to the \pkg{sdmTMB} model structure.
A subset of features to be added in the near future includes (1) multivariate
models to allow for simultaneous modelling of data from multiple species, (2)
integration with the \pkg{RTMB} \citep{rtmb} package so that the model code base
will be written in \proglang{R} rather than \proglang{C++}, (3) inclusion of
a dispersion formula similar to \pkg{glmmTMB}, and (4) estimation of random
slopes.
% TODO random slopes looks gnarly to do generically?
